G\"{o}del's God on the Computer\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2013-11-04 Abstract/IWIL-2013/abstract.tex
Abstract for IWIL

Furthermore, the multi-step THF development of the proof has
recently been encoded in Sutcliffe's new TPI scripting
language~\cite{}. This scripting language offers important features
that were missing in the TPTP world so far. Our collaboration with
Sutcliffe has also led to some improvements of the TPI langauge.

@@

>>>>

Furthermore, the multi-step THF development of the proof has
recently been encoded in Sutcliffe's new TPI scripting
language~\cite{TPI}. This scripting language offers important features
that were missing in the TPTP world so far. Our collaboration with
Sutcliffe has also led to some improvements of the TPI language.

@@

\bibitem{THF}
G.~Sutcliffe.
\newblock The TPTP TPI Scripting Language (check!).
\newblock {\em Proc. of IWIL-10}, 2013.
